On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 blind.tex
Fix some labels and references
Fix wording

\def\SampB{\mathsf{Samp, blind}}
\nc{\PiSampB}{\ensuremath{\Pi_\SampB}}

@@

\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\SampBQP$ language $L$}
	\label{proto:BlindBQP}
	Verifier's input: $x\in\set{0,1}^n$.

@@

\begin{thm}
	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
\end{thm}
\begin{prf}
	The proof of \cref{thm:BlindBQP} works, up to changing some labels.
	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either.
	The proof only shows that the compiliation preserves soundness.
\end{prf}

>>>>

\def\SampB{\mathsf{Samp, blind}}
\nc{\PiSampB}{\ensuremath{\Pi_\SampB}}
\nc{\VSampB}{\ensuremath{V_\SampB}}
\nc{\PSampB}{\ensuremath{P_\SampB}}

@@

\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\PiSampB = (\PSampB, \VSampB)$ for $\SampBQP$ language $L$}
	\label{proto:BlindSampBQP}
	Verifier's input: $x\in\set{0,1}^n$.

@@

\begin{thm}
	$\PiSampB$ has the same completeness and soundness guarantees as $\PiSamp$ and is blind.
\end{thm}
\begin{prf}
	The proof is identical to that of \cref{thm:BlindBQP} up to relabeling.
	Note that we don't have negligible soundness errors here, since $\PiSamp$ doesn't either; the proof only shows that the compiliation preserves soundness.
\end{prf}
